\documentclass[]{k-cv}

\defaultfontfeatures{Mapping=tex-text}
\usepackage{xcolor}
\addbibresource{bibliography.bib}

\begin{document}
\header{manuel}{montoya}
       {Full stack RoR/JS developer}

% In the aside, each new line forces a line break
\begin{aside}
  \section{contact}
    \href{mailto:mmontoya@gmail.com}{mmontoya@gmail.com}
    Tel  52 (55) 4168-7570
    Cell 52 (55) 2878-3910
    \href{http://github.com/aarkerio}{github://aarkerio}
    \href{https://medium.com/@mmontoya}{medium://mmontoya}
    skype://aarkerio
    Mexico City
  \section{languages}
    native spanish
	  spoken english
	  can read german

  \section{gems I use often}
    capistrano \textbf{factory}-boot \textbf{r}spec
    \textbf{bootstrap} sidekiq unicorn \textbf{hamlit} sassrails \textit{compass}
    decent\_exposure \textbf{debugger} carrierwave \textbf{devise} cells \textbf{webpacker}
    cucumber \textbf{guard} capybara \textbf{unicorn}
    \textbf{rubo}cop \textbf{react-rails}
    \textbf{will\_paginate} \textbf{database}\_cleaner

\end{aside}

\section{profile}

I'm a remote Web developer with lots of experience developing complex solutions in the e-Commerce, e-Learning, e-Health and Fintech sectors.
Last years I've been working for US and Swedish based companies. Coding clean and well planned software can be easy if you know your tools and the Domain,
not just the language. In software, design and simplicity matters.

I love coffee, hiking with my dogs, solving problems and learning new stuff, I try to learn a new language every four years. I've been
programming for eighteen fun years, since the old days when the Web was made with CGI-perl pages and ugly Java applets. Now I develop using RoR, Clojure and TypeScript with SQL and
noSQL DBs. IMO testing the code and using Continuous Integration is pretty important. Functional Programming and immutability are awesome. My daily desktop is \href{https://i3wm.org/}{i3} on Debian. I use \href{http://netbsd.org}{NetBSD} on my hobby servers because compiling from the sources is fun. I'm really good rescuing and updating legacy code that has been neglected over time. \href{https://github.com/aarkerio/ZentaurLMS/blob/master/src/cljs/zentaur/reframe/tests/events.cljs}{http://Zentaur}
is my current side project, a vClassroom Manager System built with GraphQL and ClojureScript.

As any real man, I use Emacs as my default editor ;-)

\section{summary of qualifications}
  \begin{itemize}
    \item Eighteen years of experience delivering non-trivial Web solutions, from Single Page Applications
          with React or a new SCORM player, to implementation of Archetype-based medical semantics on e-Health.
    \item Advanced OOP abstractions and use of Design Patterns with Ruby, JavaScript and PHP.
    \item Four years of experience with Amazon Web Services: EC2, DynamoDB, RDS, SQS, S3, API Gateway, Cognito and Serverless Lambda.
    \item Lots of experience installing and configuring server side services (HTTP,
          RDBMS, RabbitMQ, Subversion, Git, SMTP, SSH, FTP, DNS, LDAP ) on Linux and
          BSD servers.
    \item Aware that good communication and close collaboration inside a team
          are very important in order to create great products.
    \item Clear and patient explaining and encouraging rookie developers.
   \end{itemize}

\section{technologies I'm proficient}

    Linux (since 1997), RoR (since 2008), JavaScript (1999), Lisp, Perl, jQuery, Node.js, ReactJS, Redux, Webpack, Git,
    Github, ClojureScript, Apache, Nginx, PostgreSQL, MySQL, SQLite, Redis, Solaris,
    tmux, JSON, SSH, XML, RESTful architecture, GraphQL, Test Driven Development (rspec and jest),
    Integration Server (Jenkins), I develop under Scrum and Kanban methodologies.


\newpage

\section{education}

\begin{entrylist}
  \entry
    {1995 - 2000}
    {B. Sc. in Computer Science}
    {National University (UNAM)}
	  {Faculty of Sciences, Mexico City}
  \entry
    {June 2008}
    {OOP Design Patterns with Python}
    {JBI Training}
    {London, England}
   \entry
    {December 2010}
    {Refactoring your Rails code}
    {Global Day of Code Retreat}
    {Leipzig, Germany}

\end{entrylist}

\section{professional experience}

  \textbf{Clojure/ClojureScript/AWS Developer}  \textit{Not a Bank}
  {\color{gray} {\small Jul. 2018 - Jan. 2020 \par}}
  \begin{itemize}
    \item \textit{Not a Bank} is a startup that offers financial services trough a Cell phone App.
    \item I made the analysis and design of the GraphQL API that the new App
          requires in order to make transactions, reports and notifications. Worked with a Swedish company to improve the tokens.
    \item Together, four Clojure developers and I deployed on production the code for the \linebreak
          payments/withdrawals services.
    \item Nine services were deployed as Clojure AWS Lambdas: the App consumed a lot of different APIs.
    \item A little Web report tool for inner use was made with ClojureScript.
    \item Cognito, SES, RDS PostgreSQL, SQS, S3 and DymamodDB were used on AWS.
  \end{itemize}

  \textbf{Ruby/ReactJS Developer}  \textit{HOMIE}
  {\color{gray} {\small Sep. 2016 - Jul. 2018 \par}}
  \begin{itemize}
    \item Homie is a startup that provides Real State related services. In this project I
          worked with people from the financial and data science fields to create a new
          \textit{Risk Score Assessment Tool}.
    \item I lead a team of three remote engineers to build and launch in six months the tool
          using Rails, MongoDB, RabbitMQ and R language.
    \item Several REST and GraphQL APIs were used in order to receive online payments and extract data from social networks.
    \item I developed and deployed several services on AWS.
  \end{itemize}

   \textbf{RoR/JS Developer} \textit{Las Lomas Veterinary Clinic}
   {\color{gray} {\small Sep. 2015 - Sep. 2016 \par}}
   \begin{itemize}
     \item I developed a full Customer Management System from scratch using Webpack/React/Redux in the front end.
     \item Coded a RoR4 JSON API. I used some PostgreSQL JSONB options instead of MongoDB.
     \item Full TDD covering using Rspec and Mocha/Enzyme in the front end.
     \item The Web solution included the payroll, suppliers, appointments, taxes and invoice sections.
     \item I developed a new gem to connect the mailing list with MailChimp.
   \end{itemize}

  \textbf{Ruby Developer}  \textit{ePublishing, inc.}
  {\color{gray} {\small Mar. 2014 - Jul. 2015 \par}}
   \begin{itemize}
     \item I created a new RESTful JSON API for a pharmaceutical client with Rails 4 to
           search for medicines and medical supplies. Redis was used to store
           special offers and taxes by state.
     \item Wrote the full integration between Rails 4 and Gigya.com API services (shared
           sessions, comments, social networks).
     \item Developed a Newsletter Manager gem. I imported and normalised 300,000
           scientific articles and abstracts from different sources and formats.
     \item Coded ruby scripts to update and interchange data between several kind of
           databases using JSON files.
  \end{itemize}

   \textbf{CTO} \textit{PCSB, SA de CV}
   {\color{gray} {\small Jun. 2007 - Jan. 2014 \par}}
   \begin{itemize}
     \item Six years leading a team of four developers, a pedagogic planner and a
           graphic designer to create four big medical web sites, including a new tool to
           search, import and display medical resources (video, audio, books, magazines).
     \item I designed and coded a new and big e-Learning platform (virtual classrooms,
           chatrooms, e-tests) for a Medical Institution using Rails 3 and Postgres. I
           developed and implemented several SCORM courses.
     \item Google and Facebook APIs were used to create Docs, Sessions and Calendars
           inside the Rails platform.
   \end{itemize}

   \textbf{Developer and webmaster} \textit{University of Mexico}
   {\color{gray} {\small Sep. 2004 - May 2007 \par}}
   \begin{itemize}
     \item Maintaining and porting legacy code from PHP3 spaghetti code to OOP PHP5 using CakePHP framework.
     \item A budget/purchases system, delivering XML and PDF reports.
   \end{itemize}

   \textbf{Web Developer} \textit{Bank of Commerce (Bancomext)}
   {\color{gray} {\small Jan. 1998 - Aug. 2004 \par}}
   \begin{itemize}
     \item I designed, developed and deployed an Intranet solution using Perl and PHP
           over Solaris servers and Oracle as RDBMS.
     \item Using Perl, Apache and MySQL, I developed a Loan Management System.
     \item Coded a new Web File Sharing System.
   \end{itemize}

\end{entrylist}

\end{document}
